PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-28 qfenv_paper/qf_environment.tex
minor edit

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our sample construction, and galaxy environment measurements. In Section \ref{sec:smf} we examine the stellar mass function evolution for star-forming/quiescent and high/low density environment subsamples. In Section \ref{sec:qf_const} compare the quiescent fraction evolution in high and low density environments. In Section \ref{sec:summary} we summarize our results and discuss implications of the results on quenching mechanisms.

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
%%% INCLUDE OUTLINE OF PAPER

\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quiescent fraction over the redshift range $ z < 1.0$. For our analysis, we require a sample with sufficient depth to probe the redshift range and robust redshifts to measure galaxy environment. PRIMUS, with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis. In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.

>>>>

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our sample construction, and galaxy environment measurements. In Section \ref{sec:smf} we examine the stellar mass function evolution for star-forming/quiescent and high/low density environment subsamples. In Section \ref{sec:qf_const} we compare the quiescent fraction evolution for high and low density environments and discuss implications of the results on quenching mechanisms. In Section \ref{sec:summary} we summarize our results.

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.

\section{Sample Selection} \label{sec:sample}
In order to quantify the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis. In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.
